A Switching Planner for Combined Task and Observation Planning

### 2010-11-29 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
fixed discussions
Tiny changes to your example

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper we take $\hat\$(x)= - \$(x)(1 -
p) / p$, where $\$(x)$ is a given constant.

@@

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration.  We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Taking our example trace from earlier, we have a {\em
relaxed} declaration:

\small
\begin{tabtt}
(\=:init (= (is-in DORA) kitchen) \+ \\
       (probabilistic \=.8 (= (is-in box) office)  \\
		      \>.2 (= (is-in box) kitchen))) \\
\end{tabtt}
\normalsize

\noindent and therefore, the belief-state $\bstate_0$ is:

\small
\begin{tabular}{cccc}
\hline
Probability & (is-in DORA)  & (is-in box)  & (is-in cup) \\
\hline
.8 & kitchen & office & \# \\
.2 & kitchen & kitchen & \# \\
\hline
\end{tabular}
\normalsize

\noindent At this point, the session would proceed in an
abstraction of the environment that does not contain a
$\pp{cup}$. With regards to abstraction, the contingent and serial
sessions apply the same applicability conditions ---i.e., that each
effect and condition $\prop$ is specified, $\prop\in\state$--- to
actions from the DTPDDL problem description.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero
probability according to that refined declaration remains of a
practicable size. In detail, for each excluded atomic term, we compute
the {\em entropy} of the active assumptions, {\em conditional} on the
corresponding proposition. Loosely speaking, the {\em conditional
entropy} measure is higher the more uncertain those assumptions are
given truth assignment to the proposition. Propositions that in the
first place were excluded are iteratively added to the problem posed
to the conditional session in increasing order according to that
measure.

>>>>

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper, we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - p) / p$ where $p$ is the
probability that $x$ is true.

@@

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration. We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Figure \ref{fig:abstraction} shows the belief-state
of a more detailed version of our previous example. The diamonds
represent probabilistic terms of the state description while circles
represent conjunctive or atomic terms.

\begin{figure}[h!]
  \centering
  \tikzstyle{tree} = [sibling distance=4mm]
  \tikzstyle{toplevel} = [grow'=right, sibling distance=18mm]
  \tikzstyle{seclevel} = [sibling distance=8mm]
  \tikzstyle{pnode} = [diamond, draw=black, minimum size=2mm]
  \tikzstyle{cnode} = [circle, draw=black, minimum size=2.5mm]
  \tikzstyle{assumption} = [solid, thick, draw=black]
  \tikzstyle{selected} = [solid, draw=black]
  \tikzstyle{unused} = [densely dashed, draw=black!40]
  \subfloat[The initial belief-state with the assumptions made by the continual
    planner.]{
      \label{fig:abstraction-a}
      \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode] (cup) {} 
          child {node [cnode] (cupp1) {}}
          child {node [cnode] (cupp2) {}}
        }
      }
      child {node[cnode] (kitchen) {}
        child {node [pnode] (box2) {} 
          child {node [cnode] (box2p1) {}}
          child {node [cnode] (box2p2) {}}
        }
      };
   \tiny
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of kitchen] {$\pp{kitchen}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[below=0 of cup] {$\pp{(is-in cup)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
   \node[right=0 of cupp1] {$\pp{place1}$};
   \node[right=0 of cupp2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\qquad
  \subfloat[Remove facts that are not part of an assumption.]{
    \label{fig:abstraction-b}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, unused] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, unused] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\qquad
  \subfloat[Re-add relevant facts until the belief space limit is reached.]{
    \label{fig:abstraction-c}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, selected] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, selected] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (box) -- (boxp1);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \draw[selected] (box2) -- (box2p1);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}

  \caption{Generating the abstract belief space.}
\label{fig:abstraction}
\end{figure}

% \small
% \begin{tabtt}
% (\=:init (= (is-in DORA) kitchen) \+ \\
%        (probabilistic \=.8 (= (is-in box) office)  \\
% 		      \>.2 (= (is-in box) kitchen))) \\
% \end{tabtt}
% \normalsize

% \noindent and therefore, the belief-state $\bstate_0$ is:

% \small
% \begin{tabular}{cccc}
% \hline
% Probability & (is-in DORA)  & (is-in box)  & (is-in cup) \\
% \hline
% .8 & kitchen & office & \# \\
% .2 & kitchen & kitchen & \# \\
% \hline
% \end{tabular}
% \normalsize

 % With
% regards to abstraction, the contingent and serial sessions apply the
% same applicability conditions ---i.e., that each effect and condition
% $\prop$ is specified, $\prop\in\state$--- to actions from the DTPDDL
% problem description.

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment where that does not
contain $\pp{place2}$, the $\pp{cup}$ or a $\pp{kitchen}$.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero
probability according to that refined declaration remains of a
practicable size. In detail, for each excluded atomic term, we compute
the {\em entropy} of the active assumptions, {\em conditional} on the
corresponding proposition.  Loosely speaking, the lower the {\em
  conditional entropy} of an atom, the more information about the
assumptions the contingent planner expect to derive from it. Thus,
propositions that in the first place were excluded are iteratively
added to the problem posed to the conditional session in increasing
order according to that measure (Fig. \ref{fig:abstraction-c}).
